---
title: "Exploration of ctrialsgov: Access, Visualization, and Discovery of the ClinicalTrials.gov Database"
author: "Howard Baek"
date: "12/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r}
library(ctrialsgov)
library(tidyverse)
```

`clinicaltrials.gov` website provides a database of clinical studies from around the world. Maintained by the U.S National Library of Medicine and the NIH.

## Create the data
```{r}
# Download a static version of data and load into R
ctgov_load_cache()
```

Regardless of which way you create the data, the querying functions will work.

## Query the data
```{r}
# Primary function for querying dataset: ctgov_query()
ctgov_query(study_type = "Interventional")

# Another way to query: continuous values
ctgov_query(enrollment_range = c(40, 42))
ctgov_query(enrollment_range = c(1000, NA))

# Third way: Using keywords(kw)
ctgov_query(description_kw = "lung cancer")

ctgov_query() %>% 
  ctgov_query(description_kw = "cancer") %>% 
  ctgov_query(enrollment_range = c(100, 200)) %>% 
  ctgov_query(date_range = c("2019-01-01", "2020-02-01"))
```



## Text Analysis

```{r}
# ctgov_kwic() highlights all occurences of a term within context
z <- ctgov_query(study_type = "Interventional")
ctgov_kwic("bladder", z$brief_title, z$nct_id)

# TF-IDF
z <- ctgov_query()
tfidf <- ctgov_tfidf(z$description)
print(tfidf, n = 15)

# Document similarity
z <- ctgov_query(
  study_type = "Interventional", sponsor_type = "Industry", phase = "Phase 2"
)
scores <- ctgov_text_similarity(z$description, min_df = 0, max_df = 0.1)
dim(scores)

index <- order(scores[, 100], decreasing = TRUE)[seq_len(15)]
z$brief_title[index]
```


## Specific Analysis

```{r}
# Search for Pembrolizumab
pem <- ctgov_query(description_kw = "Pembrolizumab")

# Search for Nivolumab
niv <- ctgov_query(description_kw = "Nivolumab")

pem$outcomes[[1]]
niv$outcomes[[3]]
```

`outcomes` column is a list-column containing tibble with information on outcome type, outcome measure, time frame, and description. Measures include Objective response rate (ORR), Progression-free survival (PFS), and Overall survival (OS).
